---
title: 'DoD Fixed-Price Study: Contract Vehicle Classification'
author: "Greg Sanders"
date: "Tuesday, January 13, 2015"
output:
  html_document:
    keep_md: yes
    toc: yes
---

```{r hiddensetup, echo = FALSE}
require(ggplot2)
require(stringr)
require(plyr)
options(error=recover)
setwd("K:\\Development\\Fixed-price")
# setwd("C:\\Users\\Greg Sanders\\Documents\\Development\\Fixed-price")
Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
# Path<-"C:\\Users\\Greg Sanders\\SkyDrive\\Documents\\R Scripts and Data SkyDrive\\"
source(paste(Path,"lookups.r",sep=""))

```

Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the [exploration on R&D](RnD_1to5_exploration.md), we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..

##Studying contract vehicle within the sample.

The initial contract vehicle is primarily classified using the standard methodology for [CSIS reports](http://csis.org/program/methodology).  The significant difference from the standard CSIS methodology is that, like competition, contract vehicle is classified using the original unmodified contract transition.  In this study we determine the contract vehicle by classifying both awards and indefinite delivery vehicles (IDVs).  While classifying awards is straightforward, classifying IDVs requires the referenced IDV contract type field, which is only available via the FPDS web tool.  


```{r setup, echo = TRUE}
contract.sample  <- read.csv(
    paste("data\\defense_contract_CSIScontractID_sample_15000_SumofObligatedAmount.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )

#These will probably be moved into apply_lookups at some point
contract.sample<-apply_lookups(Path,contract.sample)
```
The study team recreates this field by automatically looking up the referenced parent IDV for each delivery order.  When this lookup is unsuccessful, typically because the IDV originated before the study period, the study team relies on tables downloaded from the FPDS web tool.  This approach may not exactly match the FPDS web tool results, but it allows for cross-tabulation, enables emulation of the DoD method for calculating competition as discussed below, and removes the discrepancies that result from the use of multiple sources.  

###IsIDV
**IsIDV is a binary variable.**

* The variable has value 1 meaning true if the contract is an indefinite delivery vehicle (IDV).
* The variable has value 0 meaning false if it is a definitive contract or a purchase order. 
* Unlabeled cases are classified as NAs.

* IsIDV is a classification for the entirity of the contract  (`r sprintf("%1.2f%%",nrow(subset(contract.sample,is.na(IsIDV))) /nrow(contract.sample)*100)` missing data).
  
```{r overallvars, echo = TRUE}
summary(subset(contract.sample,select=c(contractactiontype,
                                multipleorsingleawardidc,
                                IsIDV,
                                addmultipleorsingawardidc,
                                AwardOrIDVcontractactiontype
                                ))
        )

```
