 Dod Fixed-Price Study: Is Terminated exploration
============================================================================

```{r echo = TRUE}
##install.packages("ggplot2")

##library("ggplot2")

setwd("K:\\Development\\Fixed-price")

Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
source(paste(Path,"lookups.r",sep=""))



Coloration<-read.csv(
    paste(Path,"Lookups\\","lookup_coloration.csv",sep=""),
    header=TRUE, sep=",", na.strings="", dec=".", strip.white=TRUE, 
    stringsAsFactors=FALSE
    )

Coloration<-ddply(Coloration
                  , c(.(R), .(G), .(B))
                  , transform
                  , ColorRGB=as.character(
                      if(min(is.na(c(R,G,B)))) {NA} 
                      else {rgb(max(R),max(G),max(B),max=255)}
                      )
                  )

```

Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..

## Contract Terminations


Contract terminations and the number of change orders can be calculated for the entire sample.  Contract termination is determined using the *Reason for Modification* field in FPDS.  A contract is considered to be terminated if it has at least one modification with the following values:

* "Terminate for Default (complete or partial)"
* "Terminate for Convenience (complete or partial)"
* "Terminate for Cause"
* "Legal Contract Cancellation"

These four catetegories and the "Close Out" category are used to mark a contract as closed.  Many contracts in FPDS and in the sample are never marked closed.  




```{r echo = TRUE}
setwd("K:\\Development\\Fixed-price")

ContractWeighted  <- read.csv(
    paste("data\\defense_contract_CSIScontractID_sample_15000_SumofObligatedAmount.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )

CompleteModelAndDetail  <- read.csv(
    paste("data\\defense_contract_CSIScontractID_detail.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )


CompleteModelAndDetail$Ceil<-factor(CompleteModelAndDetail$Ceil,
                                        levels=c("[0.00e+00,1.50e+04)"
                                                 ,"[1.50e+04,1.00e+05)"
                                                 ,"[1.00e+05,1.00e+06)"
                                                 ,"[1.00e+06,3.00e+07)"
                                                 ,"[3.00e+07,3.36e+12]"
                                                 ),
                                        labels=c("[0,15k)"
                                                 ,"[15k,100k)"
                                                 ,"[100k,1m)"
                                                 ,"[1m,30m)"
                                                 ,"[30m+]"
                                                 ),
                                        ordered=TRUE)

#These will probably be moved into apply_lookups at some point
#ContractWeighted <- apply_lookups(Path,ContractWeighted)

```

**A Histogram of the IsTerminated data** showing the distribution of whether or not a contract was terminated each year from 2007.  

```{r echo = TRUE}

library("ggplot2")

ContractWeighted<-subset(ContractWeighted, StartFiscal_Year>=2007)

ggplot(
  data = ContractWeighted,
  aes_string(x = "IsTerminated"),
  ) + geom_bar(binwidth=0.5) +
facet_wrap("StartFiscal_Year")



ggplot(
  data = CompleteModelAndDetail,
  aes_string(x = "Term"),
  ) + geom_bar() + 
    facet_grid( Ceil ~ .,
                scales = "free_y",
                space = "free_y") + scale_y_continuous(expand = c(0,50)) 





ggplot(
  data = subset(CompleteModelAndDetail,Term=="Terminated"),
  aes_string(x = "Ceil")
  )+ geom_bar()+
    scale_x_discrete("Initial Cost Ceiling (Base and All Options Value")+scale_y_continuous("Number of Partially or Completely \nTerminated Contracts")






CompleteModelAndDetail$Graph[CompleteModelAndDetail$Term=="Terminated"]<-TRUE

CompleteModelAndDetail$Graph[CompleteModelAndDetail$Term=="Unterminated"]<-FALSE

CompleteModelAndDetail$ContractCount<-1
CompleteModelAndDetail<-ddply(CompleteModelAndDetail, .(Ceil), transform, pContract=ContractCount/sum(ContractCount))
CompleteModelAndDetail<-ddply(CompleteModelAndDetail, .(Ceil), transform, pObligation=Action.Obligation/sum(Action.Obligation))

head(CompleteModelAndDetail)

ggplot(
  data = subset(CompleteModelAndDetail,Term=="Terminated"),
  aes_string(x = "Ceil",weight="Action.Obligation")
  )+ geom_bar()+
    scale_x_discrete("Initial Cost Ceiling (Base and All Options Value")+scale_y_continuous("Total Obligated Value of Partially or Completely Terminated Contracts")


ggplot(
  data = subset(CompleteModelAndDetail,Term=="Terminated"),
  aes_string(x = "Ceil",weight="pContract")
#   main="Percentage of Contracts going to Partially or Completely Terminated Contracts\nBy Initial Contract Ceiling"
  )+ geom_bar()+ scale_y_continuous("Percent of Contracts by Cost Ceiling Category", labels=percent)+
    scale_x_discrete("Initial Cost Ceiling (Base and All Options Value)")


ggplot(
  data = subset(CompleteModelAndDetail,Term=="Terminated"),
  aes_string(x = "Ceil",weight="pObligation"),
  main="Percentage of Contract Obligations going to Partially or Completely Terminated Contracts\nBy Initial Contract Ceiling"
  )+ geom_bar()+ scale_y_continuous("Percent of Obligations in Cost Ceiling Category", labels=percent)+
    scale_x_discrete("Initial Cost Ceiling (Base and All Options Value)")


# 
# LatticePercentLineWrapper("VAR.name"
#                                     ,"VAR.proper.name"
#                                     ,"VAR.X.label"
#                                     ,"VAR.Y.label"
#                                     ,Coloration
#                                     ,subset(CompleteModelAndDetail,!is.na(Term))
#                                     ,NULL
#                                     ,"Ceil"
#                                     ,"Count"
#                                     ,"Term"
#                                     ,NA
#                                     ,NA
#                                     )


+ 
    facet_grid( Ceil ~ .,
                scales = "free_y",
                space = "free_y") 


head(CompleteModelAndDetail)
```



