---
title: 'DoD Fixed-Price Study: Product, Service, or R&D'
author: "Greg Sanders"
date: "Tuesday, January 13, 2015"
output:
  html_document:
    keep_md: yes
    toc: yes
---

```{r hiddensetup, echo = FALSE}
require(ggplot2)
require(stringr)
require(plyr)
options(error=recover)
setwd("K:\\Development\\Fixed-price")
# setwd("C:\\Users\\Greg Sanders\\Documents\\Development\\Fixed-price")
Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
# Path<-"C:\\Users\\Greg Sanders\\SkyDrive\\Documents\\R Scripts and Data SkyDrive\\"
source(paste(Path,"lookups.r",sep=""))

```

Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the [exploration on R&D](RnD_1to5_exploration.md), we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..

##Studying contract: product, service or research and design.

One contract characteristic we study is the type of product or service being procured; a product, service or R&D.  This classification can be derived from a single field of the database, using groupings established by the study team.  The mixed and unlabeled category includes contracts that report categories of product and service codes at various points during the lifespan on the contract.   

```{r setup, echo = TRUE}
contract.sample  <- read.csv(
    paste("data\\defense_contract_CSIScontractID_sample_15000_SumofObligatedAmount.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )

#These will probably be moved into apply_lookups at some point
contract.sample<-apply_lookups(Path,contract.sample)
```
Describe source variables in FPDS here. #??

###IsIDV ??
Is IDV is a binary variable, true if the contract is an indefinite delivery vehicle (IDV), false if it a definitive contract or a purchase order. Unlabeled cases are classified as NAs.

* simplearea is a classification for the entirity of the contract  (`r sprintf("%1.2f%%",nrow(subset(contract.sample,is.na(simplearea))) /nrow(contract.sample)*100)` missing data).
  
```{r overallvars, echo = TRUE}
summary(subset(contract.sample,select=c(simplearea
                                ))
        )

```
