---
title: "ContractTermination"
author: "Greg Sanders"
date: "Friday, March 20, 2015"
output:
  html_document:
    keep_md: yes
--- 

Dod Fixed-Price Study: Is Terminated exploration
============================================================================

```{r InputFiles, echo = TRUE}
##install.packages("ggplot2")

##library("ggplot2")
# 
setwd("K:\\Development\\Fixed-price")

Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
source(paste(Path,"lookups.r",sep=""))
source(paste(Path,"helper.r",sep=""))
source("ContractCleanup.r")

require(ggplot2)
require(scales)
require(Hmisc)
Coloration<-read.csv(
    paste(Path,"Lookups\\","lookup_coloration.csv",sep=""),
    header=TRUE, sep=",", na.strings="", dec=".", strip.white=TRUE, 
    stringsAsFactors=FALSE
    )

Coloration<-ddply(Coloration
                  , c(.(R), .(G), .(B))
                  , transform
                  , ColorRGB=as.character(
                      if(min(is.na(c(R,G,B)))) {NA} 
                      else {rgb(max(R),max(G),max(B),max=255)}
                      )
                  )

```

Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..

## Contract Terminations


Contract terminations and the number of change orders can be calculated for the entire sample.  Contract termination is determined using the *Reason for Modification* field in FPDS.  A contract is considered to be terminated if it has at least one modification with the following values:

* "Terminate for Default (complete or partial)"
* "Terminate for Convenience (complete or partial)"
* "Terminate for Cause"
* "Legal Contract Cancellation"

These four catetegories and the "Close Out" category are used to mark a contract as closed.  Many contracts in FPDS and in the sample are never marked closed.  




```{r ReadInData, echo = TRUE}

ContractWeighted  <- read.csv(
    paste("data\\defense_contract_CSIScontractID_sample_15000_SumofObligatedAmount.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )

CompleteModelAndDetail  <- read.csv(
    paste("data\\defense_contract_CSIScontractID_detail.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )

CompleteModelAndDetail<-FormatContractModel(CompleteModelAndDetail)

#ContractWeighted <- apply_lookups(Path,ContractWeighted)

```

**A Histogram of the IsTerminated data** showing the distribution of whether or not a contract was terminated each year from 2007.  

```{r ContractTerminationGraphs, echo = TRUE, fig.width=4.5,fig.height=6}



ContractWeighted<-subset(ContractWeighted, StartFiscal_Year>=2007)


ggplot(
  data = ContractWeighted,
  aes_string(x = "IsTerminated"),
  ) + geom_bar(binwidth=0.5) +
facet_wrap("StartFiscal_Year")



ggplot(
  data = CompleteModelAndDetail,
  aes_string(x = "Term"),
  ) + geom_bar() + 
    facet_grid( Ceil ~ .,
                scales = "free_y",
                space = "free_y") + scale_y_continuous(expand = c(0,50)) 





ggplot(
  data = subset(CompleteModelAndDetail,Term=="Terminated"),
  aes_string(x = "Ceil")
  )+ geom_bar()+
    scale_x_discrete("Original Ceiling (Current $ Value)")+scale_y_continuous("Number of Partially or Completely \nTerminated Contracts",labels = comma)+theme(axis.text.x=element_text(angle=90,size=12))






CompleteModelAndDetail$Graph[CompleteModelAndDetail$Term=="Terminated"]<-TRUE

CompleteModelAndDetail$Graph[CompleteModelAndDetail$Term=="Unterminated"]<-FALSE


head(CompleteModelAndDetail)

ggplot(
  data = subset(CompleteModelAndDetail,Term=="Terminated"),
  aes(x = Ceil,weight=Action.Obligation/1000000000)
  )+ geom_bar()+
    scale_x_discrete("Original Ceiling (Current $ Value)")+scale_y_continuous("Obligations to Partially or Completely\nTerminated Contracts (Current $ Billions)",labels = comma)+theme(axis.text.x=element_text(angle=90,size=12))


ggplot(
  data = subset(CompleteModelAndDetail,Term=="Terminated"),
  aes_string(x = "Ceil",weight="pContract")
#   main="Percentage of Contracts going to Partially or Completely Terminated Contracts\nBy Initial Contract Ceiling"
  )+ geom_bar()+ scale_y_continuous("Percent of Contracts Partially or Completely Terminated\nby Original Ceiling Category", labels=percent)+
    scale_x_discrete("Original Ceiling (Current $ Value)")+theme(axis.text.x=element_text(angle=90,size=12))


ggplot(
  data = subset(CompleteModelAndDetail,Term=="Terminated"),
  aes_string(x = "Ceil",weight="pObligation"),
  main="Percentage of Contract Obligations going to Partially or Completely Terminated Contracts\nBy Initial Contract Ceiling"
  )+ geom_bar()+ scale_y_continuous("Percent of Obligations to Terminated Contracts \nin Original Ceiling Category", labels=percent)+
    scale_x_discrete("Original Ceiling (Current $ Value)")+theme(axis.text.x=element_text(angle=90,size=12))


# 
# LatticePercentLineWrapper("VAR.name"
#                                     ,"VAR.proper.name"
#                                     ,"VAR.X.label"
#                                     ,"VAR.Y.label"
#                                     ,Coloration
#                                     ,subset(CompleteModelAndDetail,!is.na(Term))
#                                     ,NULL
#                                     ,"Ceil"
#                                     ,"Count"
#                                     ,"Term"
#                                     ,NA
#                                     ,NA
#                                     )

# 
# + 
#     facet_grid( Ceil ~ .,
#                 scales = "free_y",
#                 space = "free_y") 
# 

head(CompleteModelAndDetail)
```


```{r ImportanceOfEndOfPeriod}




TerminatedEndSummary<-ddply(subset(CompleteModelAndDetail,StartFiscalYear>=2007 & 
                  StartFiscalYear<2014 &
                  !is.na(Ceil)&
                  !is.na(EndAfterPeriod)),
                            .(Ceil,
                                                  EndAfterPeriod,
                                                  Term,
                                                  StartFiscalYear
                                             ),plyr::summarise,
      Action.Obligation=sum(Action.Obligation),
      Count=length(CSIScontractID)
      )

TerminatedEndSummary<-ddply(TerminatedEndSummary,.(Ceil,
                                                  EndAfterPeriod,
                                             StartFiscalYear
                                             ),transform,
                      pContractCeilDurStart=Count/sum(Count),
                      pObligationCeilDurStart=Action.Obligation/sum(Action.Obligation)
      )



ggplot(TerminatedEndSummary,
       aes(x=StartFiscalYear,
           y=Count,
           color=Term))+geom_line()+geom_point()+facet_grid(Ceil ~ EndAfterPeriod ) +scale_y_log10()

```


```{r AnnualTerminationRate}

CompleteModelAndDetail$TermNum<-as.integer(as.character(factor(CompleteModelAndDetail$Term,
                                  levels=c("Terminated","Unterminated"),
                                  labels=c(1,0))))



TerminatedDurSummary<-ddply(subset(CompleteModelAndDetail,StartFiscalYear>=2007 & 
                  StartFiscalYear<2014 &
                  !is.na(Ceil)&
                  UnmodifiedCompletionDate<as.Date("2013-09-30")&
                      !is.na(Term)),
                            .(Ceil,
                              Dur,
                              StartFiscalYear,
                              Term
                            ),
                            plyr::summarise,
                            Action.Obligation=sum(Action.Obligation),
                            Count=length(CSIScontractID)
                  )


TerminatedDurSummary<-ddply(TerminatedDurSummary,.(Ceil,
                                                  Dur,
                                             StartFiscalYear
                                             ),transform,
                      pContractCeilDurStart=Count/sum(Count),
                      pObligationCeilDurStart=Action.Obligation/sum(Action.Obligation)
      )


ggplot(TerminatedDurSummary,
       aes(x=StartFiscalYear,
           y=Count,
           color=Term))+geom_line()+geom_point()+facet_grid(Ceil ~ Dur ) +scale_y_log10(labels=scales::comma)



TerminatedDurStat<-ddply(subset(CompleteModelAndDetail,
                                StartFiscalYear>=2007 & 
                                    StartFiscalYear<2014 &
                                    !is.na(Ceil) &
                                    UnmodifiedCompletionDate<as.Date("2013-09-30")&
                                    !is.na(Term)),
                         .(Ceil,
                           Dur,
                           StartFiscalYear
                         ),
                         
                         plyr::summarise,
                         Action.Obligation=sum(Action.Obligation),
                         Count=length(CSIScontractID),
                         N    = length(TermNum),
                         mean = mean(TermNum),
                         sd   = sd(TermNum),
                         se   = sd / sqrt(N),
                         obl.mean = wtd.mean(TermNum,Action.Obligation),
                         ceil.mean = wtd.mean(TermNum,UnmodifiedContractBaseAndAllOptionsValue)
)
# 
# pd <- position_dodge(0.1) # move them .05 to the left and right
# 
# ggplot(tgc, aes(x=dose, y=len, colour=supp)) + 
#     geom_errorbar(aes(ymin=len-se, ymax=len+se), width=.1, position=pd) 

ggplot(TerminatedDurStat,aes(x=StartFiscalYear))+
    geom_line(aes(y=mean))+
    # geom_line(aes(y=ceil.mean))+
    geom_line(aes(y=obl.mean))+
    geom_point(aes(y=mean))+
    facet_grid(Ceil ~ Dur ) +
    scale_y_continuous(label=percent)+
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1) #, position=pd


ggplot(TerminatedDurStat,
       aes(x=StartFiscalYear,
           y=obl.mean))+geom_line()+geom_point()+facet_grid(Ceil ~ Dur ) +
    scale_y_continuous(label=percent)
         # geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1) #, position=pd


ggplot(TerminatedDurStat,
       aes(x=StartFiscalYear,
           y=ceil.mean))+geom_line()+geom_point()+facet_grid(Ceil ~ Dur ) +
    scale_y_continuous(label=percent)
         # geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1) #, position=pd


```


