---
title: "DoD Fixed-Price Study: Contract Pricing classification"
author: "Greg Sanders"
date: "Tuesday, January 13, 2015"
output:
  html_document:
    keep_md: yes
---

```{r hiddensetup, echo = FALSE}
require(ggplot2)
require(stringr)
require(plyr)
options(error=recover)
setwd("K:\\Development\\Fixed-price")
# setwd("C:\\Users\\Greg Sanders\\Documents\\Development\\Fixed-price")
Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
# Path<-"C:\\Users\\Greg Sanders\\SkyDrive\\Documents\\R Scripts and Data SkyDrive\\"
source(paste(Path,"lookups.r",sep=""))

```

Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the [exploration on R&D](RnD_1to5_exploration.md), we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start.


##Studying Pricing Mechanism of contracts in the sample.
One of CSIS's studies is directly focused on pricing mechansisms, specifically fixed-price versus alternatives.

```{r setup, echo = TRUE}
contract.sample  <- read.csv(
    paste("data\\defense_contract_CSIScontractID_sample_15000_SumofObligatedAmount.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )

#These will probably be moved into apply_lookups at some point
# contract.sample$pIsSomeCompetition <- contract.sample$ObligatedAmountIsSomeCompetition/contract.sample$ObligatedAmount
# contract.sample$pIsSomeCompetition[is.na(contract.sample$ObligatedAmountIsSomeCompetition)] <- 0
contract.sample$MinOfEffectiveDate <- strptime(contract.sample$MinOfEffectiveDate, "%Y-%m-%d")
contract.sample<-apply_lookups(Path,contract.sample)
```
FPDS classifies competition using one variables: "Type of Contract Pricing" listed here as Pricing.Mechanism.Code.

###Pricing.Mechanism.Code
Is Fixed Price is a binary variable, true if all varieties of fixed-price contracts,  competitive procedures were used, false if they were not. Unlabeled cases are classified as NAs.

* UnmodifiedIsSomeCompetition is the classification given by the first record for the contract (`r sprintf("%1.2f%%",nrow(subset(contract.sample,UnmodifiedIsSomeCompetition=="Unlabeled")) /nrow(contract.sample)*100)` missing data).
* IsSomeCompetition is a classification for the entirity of the contract  (`r sprintf("%1.2f%%",nrow(subset(contract.sample,IsSomeCompetition=="Mixed or \nUnlabeled")) /nrow(contract.sample)*100)` missing data).
  1. A contract which is sometimes classified as competed and never classified as uncompeted is categorized as competed. 
  2. A contract which is sometimes classified as uncompeted and never classified as competed is categorized as uncompeted.
  3. A contract which was always unlabeled is categorized as Mixed or Unlabeled.
  4. A contract which was classified as both competed and uncompeted in different modifications is categorized as Combination or Unlabeled.
* pIsSomeCompetition is dollar value of all transactions that were labeled as competed divided the contracts total obligations. 

```{r overallvars, echo = TRUE}
summary(subset(contract.sample,select=c(Pricing.Mechanism.Code,
                                IsFixedPrice,
                                IsCostBased,
                                IsIncentive
                                ))
        )


ggplot(
    data = contract.sample
    aes_string(x = "pIsFixedPrice"),
    main = "Distribution by percent of dollars with some competition for mixed and unlabeled contracts."
    ) +
    geom_bar(binwidth=0.05)
```
