---
title: "ChangeOrders"
author: "Greg Sanders"
date: "Friday, March 20, 2015"
output:
  html_document:
    keep_md: yes
--- 

Dod Fixed-Price Study: Costly Change Orders 
============================================================================



```{r echo = TRUE}

if (!require("ggplot2")) {
  install.packages("ggplot2", repos="http://cran.rstudio.com/") 
  library("ggplot2")
}

require(scales)

#install.packages("ggplot2")
#library("ggplot2")


Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
source(paste(Path,"lookups.r",sep=""))


Coloration<-read.csv(
    paste(Path,"Lookups\\","lookup_coloration.csv",sep=""),
    header=TRUE, sep=",", na.strings="", dec=".", strip.white=TRUE, 
    stringsAsFactors=FALSE
    )

Coloration<-ddply(Coloration
                  , c(.(R), .(G), .(B))
                  , transform
                  , ColorRGB=as.character(
                      if(min(is.na(c(R,G,B)))) {NA} 
                      else {rgb(max(R),max(G),max(B),max=255)}
                      )
                  )

```


Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..



##Costly Change Orders: existence and number of change orders 

In the same manner as contract terminations, change orders are reported in the *reason for modification* field.  There are two values that this study counts as change orders: "Change Order" and "Definitize Change Order."  For the remainder of this report, contracts with at least one change order are called **Changed Contracts**.  

There are also multiple modifications captured in FPDS that this current study will not investigate as change orders.  These include:

* Additional World (new agreement, FAR part 6 applies)
* Supplemental Agreement for work within scope
* Exercise an Option
* Definitize Letter Contract

In addition, there are a number of other modifications that may be undertaken based on changes on the government or vendor side that are not included in this analysis. 

```{r echo = TRUE}
setwd("K:\\Development\\Fixed-price")

ContractWeighted  <- read.csv(
    paste("data\\defense_contract_CSIScontractID_sample_15000_SumofObligatedAmount.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )


CompleteModelAndDetail  <- read.csv(
    paste("data\\defense_contract_CSIScontractID_detail.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )



CompleteModelAndDetail$Ceil<-factor(CompleteModelAndDetail$Ceil,
                                        levels=c("[0.00e+00,1.50e+04)"
                                                 ,"[1.50e+04,1.00e+05)"
                                                 ,"[1.00e+05,1.00e+06)"
                                                 ,"[1.00e+06,3.00e+07)"
                                                 ,"[3.00e+07,3.36e+12]"
                                                 ),
                                        labels=c("[0,15k)"
                                                 ,"[15k,100k)"
                                                 ,"[100k,1m)"
                                                 ,"[1m,30m)"
                                                 ,"[30m+]"
                                                 ),
                                        ordered=TRUE)


#These will probably be moved into apply_lookups at some point
#ContractWeighted <- apply_lookups(Path,ContractWeighted)


```


**A histogram of the data** showing the distribution of the number of change orders each year from 2007.


```{r NumberOfChangeOrders, echo = TRUE, fig.width=4.5,fig.height=6}

library("ggplot2")

ContractWeighted<-subset(ContractWeighted, StartFiscal_Year>=2007)

ggplot(
  data = ContractWeighted,
  aes_string(x = "ChangeOrderBaseAndAllOptionsValue"),
  ) + scale_x_log10()+
 geom_bar(binwidth=0.25) +
  facet_wrap("StartFiscal_Year")



CompleteModelAndDetail$Graph[CompleteModelAndDetail$SumOfisChangeOrder>0]<-TRUE
CompleteModelAndDetail$Graph[CompleteModelAndDetail$SumOfisChangeOrder==0]<-FALSE

CompleteModelAndDetail$ContractCount<-1
CompleteModelAndDetail<-ddply(CompleteModelAndDetail, .(Ceil), transform, pContract=ContractCount/sum(ContractCount))
CompleteModelAndDetail<-ddply(CompleteModelAndDetail, .(Ceil), transform, pObligation=Action.Obligation/sum(Action.Obligation))


ggplot(
  data = subset(CompleteModelAndDetail,SumOfisChangeOrder>0),
  aes_string(x = "SumOfisChangeOrder"),
  ) + geom_bar(binwidth=1) + 
    facet_grid( Ceil ~ .,
                scales = "free_y",
                space = "free_y") + scale_y_continuous(expand = c(0,50)) +scale_x_continuous(limits=c(0,10))



ggplot(
  data = subset(CompleteModelAndDetail,SumOfisChangeOrder>0),
  aes_string(x = "Ceil")
  )+ geom_bar()+
    scale_x_discrete("Initial Cost Ceiling (Base and All Options Value)")+scale_y_continuous("Number of Contracts with Change Orders")



ggplot(
  data = subset(CompleteModelAndDetail,SumOfisChangeOrder>0),
  aes_string(x = "Ceil",weight="pContract")
#   main="Percentage of Contracts going to Partially or Completely Terminated Contracts\nBy Initial Contract Ceiling"
  )+ geom_bar()+ scale_y_continuous("Percent of Contracts with Change Orders", labels=percent)+
    scale_x_discrete("Initial Cost Ceiling (Base and All Options Value)")


ggplot(
  data =subset(CompleteModelAndDetail,SumOfisChangeOrder>0),
  aes_string(x = "Ceil",weight="pObligation"),
  main="Percentage of Contract Obligations going to Contracts with Change Orders\nBy Initial Contract Ceiling"
  )+ geom_bar()+ scale_y_continuous("Percent of Obligations in Cost Ceiling Category", labels=percent)+
    scale_x_discrete("Initial Cost Ceiling (Base and All Options Value)")


ggplot(
  data = subset(CompleteModelAndDetail,SumOfisChangeOrder>0),
  aes_string(x = "Ceil",weight="Action.Obligation")
  )+ geom_bar()+
    scale_x_discrete("Initial Cost Ceiling (Base and All Options Value)")+scale_y_continuous("Total Obligated Value of Contracts with Change Orders")

levels(CompleteModelAndDetail$Ceil)

quantile(CompleteModelAndDetail$SumOfisChangeOrder,c(0.999,0.995,0.99),na.rm=TRUE)



quantile(subset(CompleteModelAndDetail$SumOfisChangeOrder,
                    !CompleteModelAndDetail$Ceil %in% c("[0,15k)","[15k,100k)")),c(0.9,0.95,0.99),na.rm=TRUE)


quantile(subset(CompleteModelAndDetail$SumOfisChangeOrder,CompleteModelAndDetail$SumOfisChangeOrder>0&
                    CompleteModelAndDetail$Ceil!="[0,15k)"),c(0.25,0.5,0.75,0.9),na.rm=TRUE)


ecdf(subset(CompleteModelAndDetail$SumOfisChangeOrder,CompleteModelAndDetail$SumOfisChangeOrder>0))(c(0,1,2,3,4))


quantile(subset(CompleteModelAndDetail$pChangeOrderObligated,CompleteModelAndDetail$SumOfisChangeOrder>0),c(0.25,0.5,0.75,0.9),na.rm=TRUE)


ecdf(subset(CompleteModelAndDetail$pChangeOrderObligated,CompleteModelAndDetail$SumOfisChangeOrder>0))(c(-0.001,0,001,0.05,0.075,0.15))


pChangeOrderObligated
```


## Costly Change Orders Potential Change Cost 

###size of change orders measured by raise of ceiling

This study uses changes in the *Base and All Options Value Amount* as a way of tracking the potential cost of change orders.

* The *Base and All Options Value Amount* refers to the ceiling of contract costs if all available options were exercised. 
* The *Base and Exercised Value Amount* is not used because contracts are often specified such that the bulk of the eventually executed contract in dollar terms are treated as options.  In these cases, the all-inclusive value provides a better baseline for tracking growth.  
* The *Action Obligation* refers to the actual amount transferred to vendors.  This study team does not use this value because spending for change orders are not necessarily front-loaded.  For example, a change to a contract in May of 2010 could easily result in payments from May 2010 through August 2013.

The % Growth in Base and All Options Value Amount form Change Orders is calculated as follows: 

*Base and All Options Value Amount* increases for all Change Order Modifications/
*Base and All Options Value Amount* from the original unmodified contract transaction


**A histogram of the data** showing the distribution of the initial amount of the specific change order 

```{r CostCeilingRaisingChangeOrders, echo = TRUE, fig.width=4.5,fig.height=6}



ggplot(
  data = subset(CompleteModelAndDetail,SumOfisChangeOrder>0),
  aes_string(x = "pChangeOrderObligated"),
  ) + geom_bar(bin=0.01) + 
    facet_grid( Ceil ~ .,
                scales = "free_y",
                space = "free_y") +   
    scale_y_continuous("Number of Contracts with Change Orders")+
    scale_x_continuous("Percentage of Cost-Ceiling-Raising Change Orders by\nInitial Cost Ceiling (Base and All Options Value)",
                       limits=c(-1.25,1.25), labels=percent)


names(CompleteModelAndDetail)

ggplot(
  data = subset(CompleteModelAndDetail,SumOfisChangeOrder>0),
  aes_string(x = "pChangeOrderObligated")
  )+ geom_bar()+
#     scale_x_continuous("Percentage of Cost-Ceiling-Raising Change Orders by\nInitial Cost Ceiling (Base and All Options Value)")
    scale_y_continuous("Number of Contracts with Change Orders")+
        facet_grid( . ~ Ceil ) +
    scale_x_continuous("Percentage of Cost-Ceiling-Raising Change Orders by\nInitial Cost Ceiling (Base and All Options Value)",
                       limits=c(-1.25,1.25), labels=percent)



ggplot(
  data = subset(CompleteModelAndDetail,SumOfisChangeOrder>0),
  aes_string(x = "pChangeOrderObligated",weight="pContract")
  )+ geom_bar()+
#     scale_x_continuous("Percentage of Cost-Ceiling-Raising Change Orders by\nInitial Cost Ceiling (Base and All Options Value)")
    scale_y_continuous("Percent of Contracts with Change Orders", labels=percent)+
        facet_grid( . ~ Ceil ) +
    scale_x_continuous("Percentage of Cost-Ceiling-Raising Change Orders by\nInitial Cost Ceiling (Base and All Options Value)",
                       limits=c(-0.5,1), labels=percent)





ggplot(
  data = subset(CompleteModelAndDetail,SumOfisChangeOrder>0),
  aes_string(x = "Ceil",weight="pContract")
#   main="Percentage of Contracts going to Partially or Completely Terminated Contracts\nBy Initial Contract Ceiling"
  )+ geom_bar()+ scale_y_continuous("Percent of Contracts with Change Orders", labels=percent)+
    scale_x_discrete("Initial Cost Ceiling (Base and All Options Value)")


ggplot(
  data =subset(CompleteModelAndDetail,SumOfisChangeOrder>0),
  aes_string(x = "Ceil",weight="pObligation"),
  main="Percentage of Contract Obligations going to Contracts with Change Orders\nBy Initial Contract Ceiling"
  )+ geom_bar()+ scale_y_continuous("Percent of Obligations in Cost Ceiling Category", labels=percent)+
    scale_x_discrete("Initial Cost Ceiling (Base and All Options Value)")


ggplot(
  data = subset(CompleteModelAndDetail,SumOfisChangeOrder>0),
  aes_string(x = "Ceil",weight="Action.Obligation")
  )+ geom_bar()+
    scale_x_discrete("Initial Cost Ceiling (Base and All Options Value)")+scale_y_continuous("Total Obligated Value of Contracts with Change Orders")


```



