#DoD Fixed-Price and Competition Study: Costly Change Orders 



```{r echo = TRUE}
install.packages("ggplot2")

library("ggplot2")

setwd("K:\\Development\\Fixed-price")

Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
source(paste(Path,"lookups.r",sep=""))
```


Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..



##Costly Change Orders: existence and number of change orders 

In the same manner as contract terminations, change orders are reported in the *reason for modification* field.  There are two values that this study counts as change orders: "Change Order" and "Definitize Change Order."  For the remainder of this report, contracts with at least one change order are called **Changed Contracts**.  

There are also multiple modifications captured in FPDS that this current study will not investigate as change orders.  These include:

* Additional World (new agreement, FAR part 6 applies)
* Supplemental Agreement for work within scope
* Exercise an Option
* Definitize Letter Contract

In addition, there are a number of other modifications that may be undertaken based on changes on the government or vendor side that are not included in this analysis. 

```{r echo = TRUE}
setwd("K:\\Development\\Fixed-price")

ContractWeighted  <- read.csv(
    paste("data\\defense_contract_CSIScontractID_sample_15000_SumofObligatedAmount.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )

#These will probably be moved into apply_lookups at some point
#ContractWeighted <- apply_lookups(Path,ContractWeighted)

```


**A histogram of the data** showing the distribution of the number of change orders each year from 2007.


```{r echo = TRUE}

library("ggplot2")

ContractWeighted<-subset(ContractWeighted, StartFiscal_Year>=2007)

ggplot(
  data = ContractWeighted,
  aes_string(x = "ChangeOrderBaseAndAllOptionsValue"),
  ) + scale_x_log10()+
 geom_bar(binwidth=0.25) +
  facet_wrap("StartFiscal_Year")


```


## Costly Change Orders Potential Change Cost 

###size of change orders measured by raise of ceiling

This study uses changes in the *Base and All Options Value Amount* as a way of tracking the potential cost of change orders.

* The *Base and All Options Value Amount* refers to the ceiling of contract costs if all available options were exercised. 
* The *Base and Exercised Value Amount* is not used because contracts are often specified such that the bulk of the eventually executed contract in dollar terms are treated as options.  In these cases, the all-inclusive value provides a better baseline for tracking growth.  
* The *Action Obligation* refers to the actual amount transferred to vendors.  This study team does not use this value because spending for change orders are not necessarily front-loaded.  For example, a change to a contract in May of 2010 could easily result in payments from May 2010 through August 2013.

The % Growth in Base and All Options Value Amount form Change Orders is calculated as follows: 

*Base and All Options Value Amount* increases for all Change Order Modifications/
*Base and All Options Value Amount* from the original unmodified contract transaction


**A histogram of the data** showing the distribution of the initial amount of the specific change order 

```{r echo = TRUE}


#library("ggplot2")

#ContractWeighted<-subset(ContractWeighted, StartFiscal_Year>=2007)

ggplot(
  data = ContractWeighted,
  aes_string(x = "ChangeOrderBaseAndExercisedOptionsValue"),
  ) + scale_x_log10()+
 geom_bar(binwidth=0.25) +
  facet_wrap("StartFiscal_Year")


```







