---
title: "ContractTermination"
author: "Greg Sanders"
date: "Friday, March 20, 2015"
output:
  html_document:
    keep_md: yes
--- 

Dod Fixed-Price Study: Is Terminated exploration
============================================================================

```{r InputFiles, echo = TRUE}
##install.packages("ggplot2")

##library("ggplot2")
# 
setwd("K:\\Development\\Fixed-price")

Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
source(paste(Path,"lookups.r",sep=""))
source(paste(Path,"helper.r",sep=""))
source("ContractCleanup.r")

require(ggplot2)
require(scales)
require(Hmisc)
Coloration<-read.csv(
    paste(Path,"Lookups\\","lookup_coloration.csv",sep=""),
    header=TRUE, sep=",", na.strings="", dec=".", strip.white=TRUE, 
    stringsAsFactors=FALSE
    )

Coloration<-ddply(Coloration
                  , c(.(R), .(G), .(B))
                  , transform
                  , ColorRGB=as.character(
                      if(min(is.na(c(R,G,B)))) {NA} 
                      else {rgb(max(R),max(G),max(B),max=255)}
                      )
                  )

```

Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..

## Contract Terminations


Contract terminations and the number of change orders can be calculated for the entire sample.  Contract termination is determined using the *Reason for Modification* field in FPDS.  A contract is considered to be terminated if it has at least one modification with the following values:

* "Terminate for Default (complete or partial)"
* "Terminate for Convenience (complete or partial)"
* "Terminate for Cause"
* "Legal Contract Cancellation"

These four catetegories and the "Close Out" category are used to mark a contract as closed.  Many contracts in FPDS and in the sample are never marked closed.  




```{r ReadInData, echo = TRUE}

ContractWeighted  <- read.csv(
    paste("data\\defense_contract_CSIScontractID_sample_15000_SumofObligatedAmount.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )

CompleteModelAndDetail  <- read.csv(
    paste("data\\defense_contract_CSIScontractID_detail.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )

CompleteModelAndDetail<-FormatContractModel(CompleteModelAndDetail)

#ContractWeighted <- apply_lookups(Path,ContractWeighted)

```

**A Histogram of the IsTerminated data** showing the distribution of whether or not a contract was terminated each year from 2007.  


```{r ImportanceOfEndOfPeriod}





BiggestContracts<-subset(CompleteModelAndDetail,Ceil == "75m+")

write.csv(BiggestContracts[order(-BiggestContracts$UnmodifiedContractBaseAndAllOptionsValue),],
          "BiggestContracts.csv")




```


```{r }