---
title: 'DoD Fixed-Price and Competition Study: Single-Offer Model Building'
author: "Greg Sanders"
date: "Tuesday, January 13, 2015"
output:
  html_document:
    keep_md: yes
    toc: yes
--- 

```{r hiddensetup, echo = FALSE}
require(ggplot2)
require(stringr)
require(graph)
require(plyr)
require(Hmisc)
require(Matrix)
require(gRain)
require(gRbase)
require(methods)
require(bnlearn)
options(error=recover)
setwd("K:\\Development\\Fixed-price")
# setwd("C:\\Users\\Greg Sanders\\Documents\\Development\\Fixed-price")
Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
# Path<-"C:\\Users\\Greg Sanders\\SkyDrive\\Documents\\R Scripts and Data SkyDrive\\"
source(paste(Path,"lookups.r",sep=""))

```

Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the [exploration on R&D](RnD_1to5_exploration.md), we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..

##Studying contract vehicle within the sample.
Describe contract vehicle here.

```{r setup, echo = TRUE}
ContractSample  <- read.csv(
    paste("data\\defense_contract_CSIScontractID_sample_100000_SumofObligatedAmount.csv", sep = ""),
    header = TRUE, sep = ",", dec = ".", strip.white = TRUE, 
    na.strings = c("NULL","NA",""),
    stringsAsFactors = TRUE
    )

#These will probably be moved into apply_lookups at some point

ContractSample$pIsFixedPrice <- ContractSample$ObligatedAmountIsFixedPrice/ContractSample$SumofObligatedAmount
ContractSample$pIsFixedPrice[is.nan(ContractSample$ObligatedAmountIsFixedPrice)|is.na(ContractSample$ObligatedAmountIsFixedPrice)] <- 0

ContractSample$pIsCostBased <- ContractSample$ObligatedAmountIsCostBased/ContractSample$SumofObligatedAmount
ContractSample$pIsCostBased[is.nan(ContractSample$ObligatedAmountIsCostBased)|is.na(ContractSample$ObligatedAmountIsCostBased)] <- 0

ContractSample$pIsCombination <- ContractSample$ObligatedAmountIsCombination/ContractSample$SumofObligatedAmount
ContractSample$pIsCombination[is.nan(ContractSample$ObligatedAmountIsCombination)|is.na(ContractSample$ObligatedAmountIsCombination)] <- 0

ContractSample$pIsInternational <- ContractSample$ObligatedAmountIsInternational/ContractSample$SumofObligatedAmount
ContractSample$pIsInternational[is.na(ContractSample$ObligatedAmountIsInternational)] <- 0

ContractSample$AnyInternational<-factor(ContractSample$AnyInternational,
                                        exclude=NULL,
                                        levels=c(0,1,NA),
                                        labels=c("Just U.S.","Any\nInternational","Unlabeled")
                                        )



ContractSample$UnmodifiedDays<-as.numeric(difftime(strptime(ContractSample$UnmodifiedCurrentCompletionDate,"%Y-%m-%d")
                                                     , strptime(ContractSample$MinOfEffectiveDate,"%Y-%m-%d")
                                                     , unit="days"
        ))+1



                               
ContractSample<-apply_lookups(Path,ContractSample)




summary(subset(ContractSample,select=c(UnmodifiedIsSomeCompetition,
                                IsIDV,
                                IsFixedPrice,
                                IsCostBased,
                                UnmodifiedIsFullAndOpen,
                                ##Number connected
                                AnyInternational,
                                SimpleArea,
                                UnmodifiedContractBaseAndAllOptionsValue,
                                UnmodifiedDays,
                                UnmodifiedNumberOfOffersReceived
                                ))
        )

        
```
Describe source variables in FPDS here.

###Limiting the sample.

Because this model analyzes the number of offers on competed contracts, the first step is eliminating contracts that were not competed. This is done using the UnmodifiedIsSomeCompetetion field (see [competition exploration](contract_competition_exploration.md) for variable details). This variable has an unlabeled rate of `r sprintf("%1.2f%%",nrow(subset(ContractSample,UnmodifiedIsSomeCompetition=="Unlabeled")) /nrow(ContractSample)*100)`. As is done throughout the model, if all labeled values for the contract have are consistent, then that value is used to fill in for the blanks.

```{r ImputingForIsSomeCompetition, echo = TRUE}

#Impute missing values when labeled entries have a consistent value.
NAisSomeCompetition<-ContractSample$UnmodifiedIsSomeCompetition=="Unlabeled"&ContractSample$IsSomeCompetition!="Mixed or \nUnlabeled"
ContractSample$UnmodifiedIsSomeCompetition[NAisSomeCompetition]<-ContractSample$IsSomeCompetition[NAisSomeCompetition]
rm(NAisSomeCompetition)
```

After imputed, UnmodifiedIsSomeCompetition has a `r sprintf("%1.2f%%",nrow(subset(ContractSample,UnmodifiedIsSomeCompetition=="Unlabeled")) /nrow(ContractSample)*100)` missing data rate. This variable can now be used to narrow the sample.

```{r competedonly, echo = TRUE}
ContractSample <- ContractSample[ContractSample$UnmodifiedIsSomeCompetition=="Comp.",]
summary(subset(ContractSample,select=c(UnmodifiedIsSomeCompetition,
                                IsIDV,
                                IsFixedPrice,
                                IsCostBased,
                                UnmodifiedIsFullAndOpen,
                                ##Number connected
                                AnyInternational,
                                SimpleArea,
                                UnmodifiedContractBaseAndAllOptionsValue,
                                UnmodifiedDays,
                                UnmodifiedNumberOfOffersReceived
                                ))
        )


```


###Evidence variables
Note that these missing data rates are only for competed entries, so they will typically not match the overall unlabeled rates.

 * IsIDV is a classification for the entirity of the contract  (`r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(IsIDV))) /nrow(ContractSample)*100)` missing data). See [vehicle exploration](contract_vehicle_exploration.md) for more. Since this variable is consistently labeled, it isn't necessary to impute data or seperate out unmodified entries.
 * UnmodifiedIsFullAndOpen is the classification given by the first record for the contract (`r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(UnmodifiedIsFullAndOpen)|UnmodifiedIsFullAndOpen=="Unlabeled")) /nrow(ContractSample)*100)` missing data). See [exploration on competition](contract_competition_exploration.md) for more.
 * UnmodifiedNumberOfOffersReceived reports the Number of Offers Received according to the first reported transaction under a contract (`r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(UnmodifiedNumberOfOffersReceived)|UnmodifiedNumberOfOffersReceived==0)) /nrow(ContractSample)*100)` missing data, far too high, there must be a SQL mistake). See [exploration on competition](contract_competition_exploration.md) for more.
* simplearea is a classification for the entirity of the contract  (`r #sprintf("%1.2f%%",nrow(subset(ContractSample,SimpleArea=="Mixed or Unlabeled")) /nrow(ContractSample)*100)` missing data). See [exploration on product, service, and R&D](contract_ProductServiceRnD_exploration.md) for more.



```{r overallvars, echo = TRUE}


ContractSample$FixedOrCost[ContractSample$pIsFixedPrice>0  |
                                      ContractSample$pIsCostBased>0 | 
                                          ContractSample$pIsCombination>0]<-"Combination \nor Other"

ContractSample$FixedOrCost[ContractSample$pIsFixedPrice>=0.95|(ContractSample$IsFixedPrice=="Fixed Price" & ContractSample$pIsCombination==0)]<-"Fixed-Price"
ContractSample$FixedOrCost[ContractSample$pIsCostBased>=0.95|(ContractSample$IsCostBased==1 & ContractSample$pIsCombination==0)]<-"Cost-Based"
ContractSample$FixedOrCost<-factor(ContractSample$FixedOrCost,levels=c("Fixed-Price","Cost-Based","Combination \nor Other"))

ContractSample$AnyInternational[ContractSample$pIsInternational<=0 & 
                    ContractSample$AnyInternational=="Any\nInternational" &
                    ContractSample$UnmodifiedIsInternational==0]<-"Just U.S."

NASimpleArea<-ContractSample$SimpleArea=="Mixed or Unlabeled"&!is.na(ContractSample$UnmodifiedSimpleArea)
ContractSample$SimpleArea[NASimpleArea]<-ContractSample$UnmodifiedSimpleArea[NASimpleArea]
ContractSample$SimpleArea[ContractSample$SimpleArea=="Mixed or Unlabeled" & ContractSample$pIsProducts>0.5]<-"Products"
ContractSample$SimpleArea[ContractSample$SimpleArea=="Mixed or Unlabeled" & ContractSample$pIsServices>0.5]<-"Services"
ContractSample$SimpleArea[ContractSample$SimpleArea=="Mixed or Unlabeled" & ContractSample$pIsRnD>0.5]<-"R&D"


roundedcutoffs<-c(15000,100000,1000000,30000000)
ContractSample$qCeiling <- cut2(ContractSample$UnmodifiedContractBaseAndAllOptionsValue,cuts=roundedcutoffs)

#Impute missing values
NAisFullAndOpen<-is.na(ContractSample$UnmodifiedIsFullAndOpen)
ContractSample$UnmodifiedIsFullAndOpen[NAisFullAndOpen]<-ContractSample$IsFullAndOpen[NAisFullAndOpen]
rm(NAisFullAndOpen)

ContractSample$qDuration<-cut2(ContractSample$UnmodifiedDays,cuts=c(61,214,366))

NAnumberOfOffers<-is.na(ContractSample$UnmodifiedNumberOfOffersReceived)&!is.na(ContractSample$NumberOfOffersReceived)
ContractSample$UnmodifiedNumberOfOffersReceived[NAnumberOfOffers]<-ContractSample$NumberOfOffersReceived[NAnumberOfOffers]
rm(NAnumberOfOffers)
ContractSample$IsIDV<-factor(ContractSample$IsIDV,levels=c(0,1),labels=c("Def/Pur","IDV"))
ContractSample$SingleOffer<-factor(ContractSample$UnmodifiedNumberOfOffersReceived==1,
                                   levels=c(TRUE,FALSE),
                                   labels=c("Single","Multi")
)

summary(subset(ContractSample,select=c(UnmodifiedIsSomeCompetition,
                                IsIDV,
                                FixedOrCost,
                                UnmodifiedIsFullAndOpen,
                                ##Number connected
                                AnyInternational,
                                SimpleArea,
                                qCeiling,
                                qDuration,
                                UnmodifiedNumberOfOffersReceived
                                ))
        )
```
The model has nine core variables, though one is presently missing. After renaming the variables, all unlabeled data is removed from the final model dataset.

*IDV (IsIDV) IsDefiniteVehicle has ('r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(IsIDV)|IsIDV=="Unlabeled")) /nrow(ContractSample)*100)` missing data.
   
* FxCb (FixedOrCost) FixedOrCost has ('r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(FixedOrCost)|FixedOrCost=="Unlabeled")) /nrow(ContractSample)*100)` missing data.

* FnO (UnmodifiedIsFullAndOpen) UnmodifiedIsFullAndOpen has (`r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(UnmodifiedIsFullAndOpen)|UnmodifiedIsFullAndOpen=="Unlabeled")) /nrow(ContractSample)*100)` missing data.

* Intl (AnyInternational) AnyInternational has (`r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(AnyInternational)|AnyInternational=="Unlabeled")) /nrow(ContractSample)*100)` missing data. 
	* PSR (SimpleArea) SimpleArea has (`r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(SimpleArea)|SimpleArea=="Unlabeled")) /nrow(ContractSample)*100)` missing data.
	* Ceil (qCeiling) qCeiling has (`r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(UnmodifiedContractBaseAndAllOptionsValue)|UnmodifiedContractBaseAndAllOptionsValue=="Unlabeled")) /nrow(ContractSample)*100)` missing data.
	* Dur (qDuration) qDuration has ('r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(MinOfSignedDate)|MinOfSignedDate=="Unlabeled")) /nrow(ContractSample)*100)` missing data.
	* Dur (LastUltimateCompleteDate) LastUltimateCompleteDate has (`r sprintf("%1.2f%%", nrow(subset(ContractSample,is.na(LastUltimateCompletionDate)|LastUltimateCompletionDate=="Unlabeled")) /nrow(ContractSample)*100)` missing data.
	

* One (SingleOffer)  UnmodifiedNumberOfOffersReceived has (`r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(UnmodifiedNumberOfOffersReceived)|UnmodifiedNumberOfOffersReceived==0)) /nrow(ContractSample)*100)` missing data.

summary(subset(ContractSample,select=c(UnmodifiedIsSomeCompetition,
                                IsIDV,
                                FixedOrCost,
                                UnmodifiedIsFullAndOpen,
                                ##Number connected
                                AnyInternational,
                                SimpleArea,
                                qCeiling,
                                qDuration,
                                UnmodifiedNumberOfOffersReceived
                                ))
        )
```
The model has nine core variables, though one is presently missing. After renaming the variables, all unlabeled data is removed from the final model dataset.

*IDV (IsIDV) IsDefiniteVehicle has ('r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(IsIDV)|IsIDV=="Unlabeled")) /nrow(ContractSample)*100)` missing data.

* FxCb (FixedOrCost) FixedOrCost has ('r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(FixedOrCost)|FixedOrCost=="Unlabeled")) /nrow(ContractSample)*100)` missing data.

* FnO (UnmodifiedIsFullAndOpen) UnmodifiedIsFullAndOpen has (`r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(UnmodifiedIsFullAndOpen)|UnmodifiedIsFullAndOpen=="Unlabeled")) /nrow(ContractSample)*100)` missing data).

* Intl (AnyInternational) AnyInternational has (`r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(AnyInternational)|AnyInternational=="Unlabeled")) /nrow(ContractSample)*100)` missing data. 

* PSR (SimpleArea) SimpleArea has (`r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(SimpleArea)|SimpleArea=="Unlabeled")) /nrow(ContractSample)*100)` missing data.

* Ceil (qCeiling) qCeiling has (`r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(UnmodifiedContractBaseAndAllOptionsValue)|UnmodifiedContractBaseAndAllOptionsValue=="Unlabeled")) /nrow(ContractSample)*100)` missing data.

* Dur (qDuration) qDuration has ('r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(MinOfSignedDate)|MinOfSignedDate=="Unlabeled")) /nrow(ContractSample)*100)` missing data.

* Dur (LastUltimateCompleteDate) LastUltimateCompleteDate has (`r sprintf("%1.2f%%", nrow(subset(ContractSample,is.na(LastUltimateCompletionDate)|LastUltimateCompletionDate=="Unlabeled")) /nrow(ContractSample)*100)` missing data.

>>>>>>> 27b71e8ed2ac0f7a1e33d77d89b15f6f9bb22e71
* One (SingleOffer)  UnmodifiedNumberOfOffersReceived has (`r sprintf("%1.2f%%",nrow(subset(ContractSample,is.na(UnmodifiedNumberOfOffersReceived)|UnmodifiedNumberOfOffersReceived==0)) /nrow(ContractSample)*100)` missing data.

The shortened names are used for ease of graphical and tabular representation. However, there exact form is still wide open, please make suggestions. Ease of comprehensibility and minimizing confusion between competing variables is key.

```{r ModelConsolidation, echo = TRUE}
ContractModel<-subset(ContractSample,select=c(IsIDV,
                                FixedOrCost,
                                UnmodifiedIsFullAndOpen,
                                ##Number connected
                                AnyInternational,
                                SimpleArea,
                                qCeiling,
                                qDuration,
                                SingleOffer
                                ))
# 

colnames(ContractModel)[colnames(ContractModel)=="IsIDV"]<-"IDV"
colnames(ContractModel)[colnames(ContractModel)=="FixedOrCost"]<-"FxCb"
colnames(ContractModel)[colnames(ContractModel)=="UnmodifiedIsFullAndOpen"]<-"FnO"
colnames(ContractModel)[colnames(ContractModel)=="AnyInternational"]<-"Intl"
colnames(ContractModel)[colnames(ContractModel)=="SimpleArea"]<-"PSR"
colnames(ContractModel)[colnames(ContractModel)=="qCeiling"]<-"Ceil"
colnames(ContractModel)[colnames(ContractModel)=="qDuration"]<-"Dur"
colnames(ContractModel)[colnames(ContractModel)=="SingleOffer"]<-"One"


nrow(ContractModel)
summary(nrow(subset(ContractModel,complete.cases(ContractModel))))
summary(subset(ContractModel,complete.cases(ContractModel)))

dropped<-subset(ContractModel,!complete.cases(ContractModel)|
           FnO=="Unlabeled"|
           Intl=="Unlabeled"|
           PSR =="Mixed or Unlabeled")

ContractModel<-subset(ContractModel,complete.cases(ContractModel)&
           FnO!="Unlabeled"&
           Intl!="Unlabeled"&
           PSR !="Mixed or Unlabeled")
nrow(ContractModel)
```

The last stage before Bayesian learning is setting the whitelists and blacklists. The whitelist contains vectors that must existing in the graph while the blacklist contains forbidden vectors. There was some iteration in the development of the white and blacklist, as nonsensical connections were removed and the blacklist was made systematic.

I've listed them below based on the origin piece of evidence.
1. IDV (IsIDV)
* Whitelist to FnO (UnmodifiedIsFullAndOpen) as many forms of IDVs don't qualify for full and open.
* Blacklist to PSR (SimpleArea) because what you are buying is picked before how you are buying it.
2. FxCb (FixedOrCost)
* Whitelist to One (SingleOffer) as this is the key study question.
* Blacklist to PSR (SimpleArea) and Intl (AnyInternational) because figuring out what and where come first.
* Blacklist to Ceil (qCeiling) and Dur (qDuration), because project scope should come before project pricing,  although this may not be entirely true when the vendors make proposals.
3. FnO (UnmodifiedIsFullAndOpen)  
* Whitelist to One (SingleOffer). We'll see how strong this connection ends up being, but it's really straightforward.
* Blacklist to PSR (SimpleArea),  Intl (AnyInternational), and FxCb (FixedOrCost), as I think those details are set before deciding competition procedures.
4. Intl (AnyInternational) No restrictions or requirements.
5. PSR (SimpleArea)
* Blacklist to Intl (AnyInternational) As I think the place of performance in the U.S. or abroad (but not the vendor location) is sometimes decided at least as early as the  product or service.
6. Ceil (qCeiling)
* Blacklist to PSR (SimpleArea) Intl (AnyInternational) because what and where come before scope.
7. Dur (qDuration)
* Blacklist to PSR (SimpleArea) Intl (AnyInternational) because what and where come before scope.
8. One (SingleOffer) 
* Blacklist to everything not covered by an existing whitelist. While the vendors responses may influence some factors at the margin, this is the dependent variable for this part of the study.

```{r BayesianLearningSetup, echo = TRUE}
#White list, connections that must occur
ContractWL<-data.frame(from="IDV",to="FnO")
ContractWL<-rbind(ContractWL,data.frame(from="FnO",to="One"))
ContractWL<-rbind(ContractWL,data.frame(from="PSR",to="FxCb"))
ContractWL<-rbind(ContractWL,data.frame(from="FxCb",to="One"))
#Black list, connections that are prohibited
ContractBL<-data.frame(from=c("One"),to= c("IDV"))
ContractBL<-rbind(ContractBL,data.frame(from="One",to="PSR"))
ContractBL<-rbind(ContractBL,data.frame(from="One",to="Intl"))
ContractBL<-rbind(ContractBL,data.frame(from="One",to="FxCb"))
ContractBL<-rbind(ContractBL,data.frame(from="One",to="Ceil"))
ContractBL<-rbind(ContractBL,data.frame(from="One",to="Dur"))
ContractBL<-rbind(ContractBL,data.frame(from="FxCb",to="PSR"))
ContractBL<-rbind(ContractBL,data.frame(from="FxCb",to="Intl"))
ContractBL<-rbind(ContractBL,data.frame(from="FxCb",to="Ceil"))
ContractBL<-rbind(ContractBL,data.frame(from="FxCb",to="Dur"))
ContractBL<-rbind(ContractBL,data.frame(from="Ceil",to="PSR"))
ContractBL<-rbind(ContractBL,data.frame(from="Ceil",to="Intl"))
ContractBL<-rbind(ContractBL,data.frame(from="Dur",to="PSR"))
ContractBL<-rbind(ContractBL,data.frame(from="Dur",to="Intl"))
ContractBL<-rbind(ContractBL,data.frame(from="FnO",to="PSR"))
ContractBL<-rbind(ContractBL,data.frame(from="FnO",to="Intl"))
ContractBL<-rbind(ContractBL,data.frame(from="FnO",to="Ceil"))
ContractBL<-rbind(ContractBL,data.frame(from="FnO",to="Dur"))
ContractBL<-rbind(ContractBL,data.frame(from="FnO",to="FxCb"))
ContractBL<-rbind(ContractBL,data.frame(from="IDV",to="PSR"))
ContractBL<-rbind(ContractBL,data.frame(from="IDV",to="Intl"))
ContractBL<-rbind(ContractBL,data.frame(from="PSR",to="Intl"))
```

After the team developed the initial list and a small number of elements accidentally left off were corrected for, the next step was to do a preliminary run through with Bayesian learning. 

```{r BayesianFirstStep, echo = TRUE}
gs_dug<-gs(ContractModel,blacklist=ContractBL,whitelist=ContractWL)
plot(gs_dug,main="Greedy first run")
```

Noteably this initial run through produced two warnings of challenging relationships IDV to Dur and IDV to FxCb. After consulting within the team, the choice was made to add whitelisted relationships that went against those automatically produced.

IDV (IsIDV) new white lists:
* Whitelist to FxCb (FixedOrCost) because the pricing mechanism of most IDVs are set. Thus, once the choice of which IDV to use is made, the pricing mechanism would be set automatically. Furthermore, Fixed-price is often the mechanism because the IDV allows for multiple instances of a single contract reducing the need for the flexabilit Cost-Based contracts offer.
* Whitelist to Dur (Duration) because the use of the IDV mechanism typically means multiple shorter contractors under one IDV rather than a single longer contract. 

With those two connections in hand, all three Bayesian Learning algorith were applied.

```{r BayesianExecution, echo = TRUE}
#White list, connections that must occur
ContractWL<-rbind(ContractWL,data.frame(from="IDV",to="Dur"))
ContractWL<-rbind(ContractWL,data.frame(from="IDV",to="FxCb"))


gs_dug<-gs(ContractModel,blacklist=ContractBL,whitelist=ContractWL)
plot(gs_dug,main="Greedy second run")
iamb_dug<-iamb(ContractModel,blacklist=ContractBL,whitelist=ContractWL)
plot(iamb_dug,main="IAMB")
iiamb_dug<-iamb(ContractModel,blacklist=ContractBL,whitelist=ContractWL)
plot(iiamb_dug,main="Inter-IAMB")
# 
